Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Polish Michael's polishing of section 1; add some Multiple Intelligences stuff.

\section{A Lesson from Nell}
\begin{figure}
\centering
\epsfig{file=xo3-3.eps, width=3.2in}
\caption{Nell's solar-powered hardware platform.  The tablet design
  allows for direct interaction.}\label{fig:xo3}
\end{figure}
% tell a nell story up front
Miles from the nearest school, a young Ethiopian girl named Rahel turns on her
new tablet computer. The solar-powered machine greets her:
\textit{``Hello!  Would you like to hear a story?''}

She nods and listens to a story about a princess.  Later, when
the Rahel has learned a little more, she will tell the machine that the
princess is named ``Rahel'' like she is and she will change the princess'
colors---but for now the green book draws pictures of the unnamed Princess for
her and asks her to trace shapes on the screen.

@@

As she traces the R, it comes to life and gallops across the screen.
\textit{``Run starts with R.  Roger the R runs across the Red Rug.
Roger has a dog named Rover.''}  Rover barks: \textit{``Ruff! Ruff!''}  The
Princess asks, \textit{``Can you find something Red?''} and Rahel uses the
camera to photograph the red stripe on a nearby Ethiopian flag.

@@

As Rahel grows, the book asks her to trace not just letters, but whole
words.  The book's responses are written on the screen as it speaks
them, and eventually she doesn't need to leave the sound on all the
time.  Soon Rahel can write complete sentences in her special book,
and sometimes the Princess will respond to them.  New stories teach her about
music (she unlocks a dungeon door by playing certain tunes) and
programming with blocks (Princess Rahel helps a not-very-bright turtle
to draw different shapes).  Rahel writes her own stories about the Princess,
which she shares with her friends.

An older Rahel learns that the block language she used to talk with
the turtle is also used to write all the software running inside
her special book.  The stories Rahel writes can now include new
functionality that make her book even more exciting for the kids
just now receiving their own green meta books.

>>>>

\section{A Lesson from Nell}
\begin{figure}
\centering
\epsfig{file=xo3-3.eps, width=3.2in}
\caption{Nell's solar-powered hardware platform.  The tablet design
  allows for direct interaction.}\label{fig:xo3}
\end{figure}
% tell a nell story up front
Miles from the nearest school, a young Ethiopian girl named Rahel turns on her
new tablet computer. The solar-powered machine speaks to her:
\textit{``Hello!  Would you like to hear a story?''}

She nods and listens to a story about a princess.  Later, when
the Rahel has learned a little more, she will tell the machine that the
princess is named ``Rahel'' like she is, and that she likes to wear blue---but
for now the green book draws pictures of the unnamed Princess for
her and asks her to trace shapes on the screen.

@@

As she traces the R, it comes to life and gallops across the screen.
\textit{``Run starts with R.  Roger the R runs across the Red Rug.
Roger has a dog named Rover.''}  Rover barks: \textit{``Ruff! Ruff!''}  The
Princess asks, \textit{``Can you find something Red?''} and Rahel uses the
camera to photograph berries on a nearby bush.

@@

As Rahel grows, the book asks her to trace not just letters, but whole
words.  The book's responses are written on the screen as it speaks
them, and eventually she doesn't need to leave the sound on all the
time.  Soon Rahel can write complete sentences in her special book,
and sometimes the Princess will respond to them.  New stories teach her about
music (she unlocks a dungeon door by playing certain tunes) and
programming with blocks (Princess Rahel helps a not-very-bright turtle
to draw different shapes).  Rahel writes her own stories about the Princess,
which she shares with her friends.  The book tells her that she is
very good at music, and her lessons begin to encourage her to invent
silly songs about what she's learning.

An older Rahel learns that the block language she used to talk with
the turtle is also used to write all the software running inside
her special book.  Rahel begins to write stories with different
kinds of new music functionality, which make the green book even more
exciting for her younger brother and the other younger kids just now
receiving them.
